Graph Product Structure for Non-Minor-Closed Classes

### 2022-03-19 slides/slides.tex
Pfffft

\title{Graph Product Structure for Non-Minor-Closed Classes}
\author{Vida Dujmović \and Pat Morin \and David R. Wood}
\titlegraphic{\includegraphics[height=1em]{by}}

@@

\begin{frame}
    \frametitle{Outline}

    \begin{itemize}
        \item $k$-planar graphs
        \item $(k,d)$-shortcut systems
        \item statement of main theorem
        \item applications
        \item proof of main theorem
        \item open problem
    \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Main Theorem}
  \framesubtitle{If $G$ has product structure then so does $G^{\mathcal{P}}$}
  \textbf{Main Theorem:} \newline
  If $G\subseteq H\boxtimes P\boxtimes K_\ell$
  \begin{itemize}
    \item  $\tw(H)\le t$
    \item $\mathcal{P}$ is a $(k,d)$-shortcut system for $G$
  \end{itemize}
  then $G^\mathcal{P}\subseteq H'\boxtimes P\boxtimes K_{\ell'}$
  \begin{itemize}
    \item $\tw(H') \le t'=\binom{k+t}{t}-1$ and
    \item $\ell'=d\ell(k^3+3k)$
    % \item $K'$ is a clique of order $d\ell(k^3+3k)$
  \end{itemize}
  \vspace{1cm}
  \uncover<2->{\textbf{Example:} $G'$ is ${\color{red} k}$-planar
    \begin{itemize}
      \item $t=3$, $\ell=3$, $d=2$, $k={\color{red}k}+1$
      \item $t'=O(k^3)$, $\ell'=O(k^3)$
    \end{itemize}
  }
\end{frame}

@@

@@

  \textbf{Lemma (Pilipczuk--Siebertz):}\footnote{Yes, the same paper!} For any $z\in V(H)$ the number of $x\in V(H)$ such that $x\prec_T z\prec_T z'$ and $\mathop{dist}_H(x,z')\le k$ is at most $\binom{k+t}{t}$.
  \begin{center}
    \multiinclude[<+>][format=pdf,start=1]{figs/pz}%
  \end{center}
  \begin{itemize}
      \item<2->Problem: $vw$-shortcut in $H\boxtimes P$ projects onto $xz'$ shortcut in $H$, but $x\not\preceq_T z'$ and $z'\not\preceq_T x$
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Lifting in $T$}
  \begin{itemize}
    \item For $v$ in $H\boxtimes P$, $a(v)$ is the LCA of $\cup\{S_I:I\in\mathcal{P'},\, v\in V(I)\}$
    \item For $x\in V(T)$, $S_x:=\{v\in V(G): a(v)=x\}$
    \begin{center}
      \includegraphics[scale=.8]{figs/nice-td-6}%
    \end{center}
    \item<2-> $\mathcal{S}:=(S_x:x\in V(T))$ is a partition of $V(G)$
    \item<3->[$(\star)$] For any $vw$-shortcut in $H\boxtimes P$, $a(v)\preceq_T a(w)$ or $a(w)\preceq_T a(v)$
\end{itemize}
\end{frame}

@@

  \begin{itemize}
      \item[$(\star)$] For any $vw$-shortcut in $H\boxtimes P$, $a(v)\preceq_T a(w)$ or $a(w)\preceq_T a(v)$
  \end{itemize}

>>>>

\title[$k$-planar product structure]{Graph Product Structure for Non-Minor-Closed Classes}
\author[Dujmović, M, Wood]{Vida Dujmović \and Pat Morin \and David R. Wood}
\titlegraphic{\includegraphics[height=1em]{by}}

@@

% \begin{frame}
%     \frametitle{Outline}
%
%     \begin{itemize}
%         \item $k$-planar graphs
%         \item $(k,d)$-shortcut systems
%         \item statement of main theorem
%         \item applications
%         \item proof of main theorem
%         \item open problem
%     \end{itemize}
% \end{frame}

@@

\begin{frame}
  \frametitle{Main Theorem}
  \framesubtitle{If $G$ has product structure then so does $G^{\mathcal{P}}$}
  \textbf{Main Theorem:} \newline
  If $G\subseteq H\boxtimes P\boxtimes K_\ell$
  \begin{itemize}
    \item  $\tw(H)\le t$
    \item $\mathcal{P}$ is a $(k,d)$-shortcut system for $G$
  \end{itemize}
  then $G^\mathcal{P}\subseteq H'\boxtimes P\boxtimes K_{\ell'}$
  \begin{itemize}
    \item $\tw(H') \le t'=\binom{k+t}{t}-1$ and
    \item $\ell'=d\ell(k^3+3k)$
    % \item $K'$ is a clique of order $d\ell(k^3+3k)$
  \end{itemize}
  \vspace{1cm}
  \uncover<2->{\textbf{Example:} $G'$ is ${\color{red} k}$-planar
    \begin{itemize}
      \item $G'\subseteq G^{\mathcal{P}}$, with $G$ planar and $\mathcal{P}$ a $(k+1,2)$-shortcut system for $G$
      \item $t=3$, $\ell=3$, $d=2$, $k={\color{red}k}+1$
      \item $t'=O(k^3)$, $\ell'=O(k^3)$
    \end{itemize}
  }
\end{frame}

@@

\begin{frame}
  \frametitle{Progress so Far}

  \begin{itemize}
    \item $\mathcal{P'}$ is a $(k,dk\ell)$-shortcut system over $H\boxtimes P$
    \item So far, $G^{\mathcal{P}}\subseteq (H\boxtimes P)^\mathcal{P'}\boxtimes K_{\ell k}$
    \item Shortcuts in $\mathcal{P'}$ project onto edges of $P$
    \item Shortcuts in $\mathcal{P'}$ project onto paths in $H$
    \item Time to study $\tw(H')$ where $H':=H^{\mathcal{P}}$
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item $(B_x:x\in V(T))$ is a nice width-$t$ tree decomposition of $H$.

    \item[]\textbf{Lemma (Pilipczuk--Siebertz):}\footnote{Yes, the same paper!} For any $z\in V(T)$ the number of $x\in V(T)$ such that $x\prec_T z\prec_T z'$ and $\mathop{dist}_H(x,z')\le k$ is at most $\binom{k+t}{t}$.
    \begin{center}
      \multiinclude[<+>][format=pdf,start=1]{figs/pz}%
    \end{center}
  \end{itemize}
  \begin{itemize}
      \item<4->Problem: $vw$-shortcut in projects onto $xz'$ shortcut in $H$, but $x\not\preceq_T z'$ and $z'\not\preceq_T x$
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Lifting in $T$}
  \begin{itemize}
    \item For $v$ in $H\boxtimes P$, $a(v)$ is the LCA of $\cup\{S_I:I\in\mathcal{P'},\, v\in V(I)\}$
    \item For $x\in V(T)$, $S_x:=\{v\in V(G): a(v)=x\}$
    \begin{center}
      \includegraphics[scale=.8]{figs/nice-td-6}%
    \end{center}
    \item<2-> $\mathcal{S}:=(S_x:x\in V(T))$ is a partition of $V(G)$
    \item<3->[$(\star)$] For any $vw$-shortcut, $a(v)\preceq_T a(w)$ or $a(w)\preceq_T a(v)$
\end{itemize}
\end{frame}

@@

  \begin{itemize}
      \item[$(\star)$] For any $vw$-shortcut, $a(v)\preceq_T a(w)$ or $a(w)\preceq_T a(v)$
  \end{itemize}
